Certified Desugaring of Javascript Programs using Coq

### 2017-01-25 paper/paper.tex
small structural changes

\newcommand{\as}[1]{\todo[color=green]{#1}}
\newcommand{\asi}[1]{\todo[color=green,inline]{#1}}
\newcommand{\mm}[1]{\todo[color=aliceblue]{#1}}
\newcommand{\mmi}[1]{\todo[color=aliceblue,inline]{#1}}

@@

A number of semantics were developed for the JavaScript language.
We are specifically interested in two of them: JSCert and \lambdajs.
In order to increase our confidence that the two semantics correctly
model JavaScript, we try to relate them formally using Coq. The size and complexity
of the two semantics makes this a complex problem with many obstacles
to be overcome.
\end{abstract}

@@

Because of the various issues we found in \lambdajs as defined
in~\cite{Politz-al:DLS12} and which we detail in Section~\ref{sec:issues},
we decided to revise the language. The full list of changes is
detailed in~TODO\mm{Can we just link the wiki page? Or should we use an appendix?}, we present some of them below.
\begin{itemize}
\item The attribute access and modification operators, which tried to directly
    model the operators from JavaScript, were removed. We found that the complexities
    of attribute access is much better handled in the desugaring.
\item We removed the imperative features of the language which do not involve the
    object heap. This change simplified the definition of the semantics, which made
    the proofs easier.
\item We added a new primitive value named \texttt{empty}, which models the empty
    completion value of JavaScript, and a second kind of the semicolon operator,
    which returns the last non-empty value of its subexpressions. This allowed to
    correctly implement statement completion values in a natural way.
\item An integer datatype was added. Even though ES5 itself has no integers,
    they are used in the definition of the binary operators (bitwise logical operators,
    bit shifting).
\end{itemize}

@@

We decided to formalize the \lambdajs core using a
pretty-big-step semantics, as in JSCert, to make the job of
relating the two semantics easier. We have also developed
an interpreter for \lambdajs, which we proved sound and
complete with respect to the pretty-big-step 
semantics.\footnote{The initial version of the interpreter was
written by Martin Lorentz.}
The proof script was developed using domain-specific tactics,
which made it simple and robust.

@@

% This was moved.
%At this stage we stumbled upon an interesting performance issue 
%involving the Coq proof assistant. The proof of completeness required
%inverting the pretty-big-step semantics judgment; this turned out
%to be very slow, and also generated large proof terms, which increased
%the memory footprint. The problem is well-known~\cite{Monin:Coq2}; 
%our solution involved
%precomputing the required inversion principles using
%\texttt{Derive Inversion}, and using the precomputed inversion
%principles to create a specialized inversion tactic.

%\asi{Put a forward pointer to a section where we described the issue in more
%  details.}

>>>>

\newcommand{\as}[1]{\todo[color=green!20]{#1}}
\newcommand{\asi}[1]{\todo[color=green!20,inline]{#1}}
\newcommand{\mm}[1]{\todo[color=aliceblue]{#1}}
\newcommand{\mmi}[1]{\todo[color=aliceblue,inline]{#1}}

@@

A number of semantics were developed for the JavaScript language.
We are specifically interested in two of them: JSCert and \lambdajs.
In order to increase our confidence that the two semantics correctly
model JavaScript, we relate them formally using Coq. The size and complexity
of the two semantics makes this a complex problem with many obstacles
to be overcome.
\end{abstract}

@@

Because of the various issues we found in \lambdajs as defined
in~\cite{Politz-al:DLS12} and which we detail in Section~\ref{sec:issues},
we decided to revise the language. The full list of changes is
detailed in~TODO\mm{Can we just link the wiki page? Or should we use an
  appendix?}\as{Let's do both: put them in the appendix, and link to the wiki.}, we present some of them below.
\begin{itemize}
\item The attribute access and modification operators, which tried to directly
    model the operators from JavaScript, were removed. We found that the complexities
    of attribute access is much better handled in the desugaring.
\item We removed the imperative features of the language which do not involve the
    object heap. This change simplified the definition of the semantics, which made
    the proofs easier.
\item We added a new primitive value named \texttt{empty}, which models the empty
    completion value of JavaScript, and a second kind of the semicolon operator,
    which returns the last non-empty value of its subexpressions. This allowed to
    correctly implement statement completion values in a natural way.
\item An integer datatype was added. Even though ES5 itself has no integers,
    they are used in the definition of the binary operators (bitwise logical operators,
    bit shifting).
\end{itemize}

@@

We decided to formalize the \lambdajs core using a
pretty-big-step semantics, as in JSCert, to make the job of
relating the two semantics easier. We have also developed
an interpreter for \lambdajs, which we proved sound and
complete with respect to the pretty-big-step 
semantics.\footnote{The initial version of the interpreter was
written by Martin Lorentz.}
The proof script was developed using domain-specific tactics,
which made it simple and robust. They are detailed in
Section~\ref{subsec:ljstactics}.

\subsection{Coq Formalization}
\label{subsec:ljscoq}

\asi{starting from the main lemmas, describe the Coq formalization, describing
  necessary details as they occur.}

@@

\subsection{Tactics}
\label{subsec:ljstactics}

\asi{Describe the tactics used in the \lambdajs proofs.}
